MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-02-12 MAESTROeX_I/paper.tex
references

science: rotation, solar physics, MHD
algorithm: SDC, high-order
implementation: GPUs

>>>>

science: rotation, solar physics, MHD

algorithm: SDC \cite{dutt2000spectral}, high-order, multi-implicit \cite{bourlioux2003high}.
Consider SDC ideas used for terrestrial combustion \cite{pazner2016high,nonaka2018conservative}

implementation: GPUs.  Forward cite next CASTRO paper with GPU strategy.
